\documentclass[11pt]{article}

\title{Use Case Description}
\author{Gavin Quinn}

\begin{document}

    \maketitle

    \section{Use Case: Multi-player}
	Players are linked together from different machines to play the game in a co-operative environment.

		\subsection{Actor(s)}
		
			Player 1 and Player 2

		\subsection{Precondition}
 
			A second user must exist before multi-player tasks and strategies can be implemented.
	
		\subsection{Description}
			\begin{enumerate}
			\item A player attempts to enter a dungeon.
			\item If they choose to play multi-player, the player is placed into a queue to await a playing partner.
			\item Both players are linked by the system, entering the dungeon in a co-operative environment. Both players are able to perform the same functions as if they were in single player, such as shopping, item use, character advancement, and environment interaction.
			\end{enumerate}

		\subsection{Postcondition}
		
			Multi-player ends when a player disconnects, or both players have agreed to exit the dungeon. It is also possible for a player to die within a dungeon during multi-player. At this time, the gameplay would revert back to a single player environment until the downed player could be revived. 

	\section{Use Case: Join Teammates}
		Players use a customized search tool to find compatible teammates. 

		\subsection{Actor(s)}
			
			Player 1 and Player 2

		\subsection{Precondition}
		
			Both players must join the "group finder" tool before they can be paired together. 

		\subsection{Description}
			\begin{enumerate}
			\item Both players enter the "find teammate" tool.
			\item The system begins searching for possible teammates, based upon current dungeon level and overall reputation standing. The system ignores possible pairings if a player is on the others "ignore" list. 
			\item The system finds a suitable match and joins the two players. 
			\end{enumerate}

		\subsection{Postcondition}

			The "group finder" is no longer being used when the two players have entered the game. At this point, the system waits until a player initiates a new search. 


\end{document}
