\documentclass[11pt]{article}

\title{Use Case Description}
\author{Abdulmajeed Alotaibi}

\begin{document}

    \maketitle

    \section{Use Case: Shop}
	Players are able to have feacher of shopping which it will have buying an item or selling an item, and all this will be through shopkeeper which player will be able to engage with.

		\subsection{Buy}
		
			There will be list of items, which the shopkeeper have and each place shopkeeper have different list of item that he/she can sell to the player. The list of items will be in box look like chat box that the player can chose the item that he/she need. Moreover, player can buy things for health, while player on compate mode and need more health the player can use that item on that time.

		\subsection{Sell}
 
			Player will be able to sell the items that player dont need it, such as old weapon or armor that player dont need it anymore. Selling will be little different then buying item when the player want to sell an item it will show list of items that player have and the player can chose what item want to sell and it will get some money from selling it.
	
		\subsection{Engage Shopkeeper}
			Shopkeeper is an NPC (Non-player character) which his job is to sell and buy items from players. It will be in different place standing waiting for players. Player will need to Engage with shopkeeper by walking to him/her and click on him/her, when the player do that the shopkeeper will show message greating the player and give the player choices if the player want to buy or sell item. If the player chose buy the shopkeeper will show the a list of items that he/she have in box and if the player chose sell the shopkeeper will show the player list of items that the player have in box.

		

\end{document}